---
title: 'Case Study: NYC Resturants Inspection'
author: "David Jackson"
date: "10/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,error=FALSE,message = FALSE)
library(tidyverse)
library(scales)
library(janitor)
library(readxl)
library(tidytext)
library(janeaustenr)
library(stringr)
library(wordcloud)
```

## Analysis of Resturants with "Critical" Violations

#### Opening Notes:

 * Grades: Grade associated with the inspection; • N = Not Yet Graded• A = Grade A• B = Grade B• C = Grade C• Z = Grade Pending• P= Grade Pending issued on re-opening following an initial inspection that resulted in a closure
 
 Since 2010, New York City has required restaurants to post letter grades that correspond to scores received from sanitary inspections. An inspection score of 0 to 13 is an A, 14 to 27 points is a B, and 28 or more points is a C. Grade cards must be posted where they can easily be seen by people passing by.
 
* score of less than 14 points on either initial or re-inspection results in an “A” grade
* On re-inspection, a score of 14-27 points means a restaurant receives both a “B” grade and a “Grade Pending” card
* On re-inspection, a score of 28 or more points means a restaurant receives both a “C” grade and a “Grade Pending” card

Source: 
* https://www1.nyc.gov/site/doh/business/food-operators/letter-grading-for-restaurants.page

* Data : https://data.cityofnewyork.us/Health/DOHMH-New-York-City-Restaurant-Inspection-Results/43nn-pn8j

#### Data Wrangling 

```{r}
rm(list=ls())
resturants <- read_excel("./nyc_restaurantsXLS.xlsx")
resturants <- janitor::clean_names(resturants)
resturants <- na.omit(resturants)
resturants$inspection_date <- lubridate::mdy(resturants$inspection_date)
resturants$score <-as.numeric(resturants$score)
resturants <- resturants %>% rename( text = violation_description)

resturants <- resturants %>% filter(inspection_date >="2014-01-01")
resturants1 <- resturants %>% filter(critical_flag =="Critical" )

```

## Discriptive Stats: Date Range Jan. 2014 - Dec. 2019

```{r}
resturants %>% count(inspection_date,sort =TRUE) %>% 
  ggplot(aes(x=inspection_date,y=n))+ geom_line() +
  geom_smooth(aes(x=inspection_date,y=n),method = "glm") +
  labs(title = "Count of Inspections by Date") 
 
```
```{r}
resturants$score <-as.numeric(resturants$score)
resturants %>% ggplot(aes(x=score)) + geom_histogram(binwidth = 20) + labs(title = "Histogram of Inspection Scores")
```

```{r}
resturants %>% count(grade,sort =TRUE) %>%
  ggplot(aes(x=reorder(grade,n),y=n)) + geom_col() +
  labs(title = "Count by Grades")
```

## Inspections were after Jan. 2014 and Flagged as Critical

```{r}
resturants1 %>% count(boro,sort =TRUE)  %>%
  ggplot(aes(x=reorder(boro,n),n)) + geom_col() +
  labs(title = "Count of Violations by Boro",x="NYC Boros",y="Count of Violations")
```

## Top Twenty Five (25) Violations by Code

```{r}
resturants1 %>% count(violation_code,sort = TRUE) %>%
  top_n(25) %>%
  ggplot(aes(x=reorder(violation_code,n),y=n)) + geom_col() +
  coord_flip() + 
  labs(title = "Top 25: by Violation Code",x="Count of Violations",
       y="Violation Code")
```

```{r}
resturants1$cuisine_description <- gsub("	
Latin (Cuban- Dominican- Puerto Rican- South & Central American)","Latin",resturants1$cuisine_description)
```
```{r}
  
resturants1 %>% count(cuisine_description,sort = TRUE) %>%
  top_n(25) %>%
  ggplot(aes(x=reorder(cuisine_description,n),y=n)) + geom_col() +
  coord_flip() + labs(title = "Top 25 Count by Cuisine")

```

## Begin Text Analysis with tidytext

```{r}
text_df <- resturants1 %>% select(text)
text_df$line <- row_number(text_df)

text_tokins <- text_df %>%
  unnest_tokens(word, text)

```
```{r}
data(stop_words)
tidy_stop <- text_tokins %>%
  anti_join(stop_words)
```

```{r}
tidy_stop %>%
  count(word, sort = TRUE) 
```

## First Visualizations

```{r}
tidy_stop %>%
  count(word, sort = TRUE) %>%
  top_n(25) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word)) +
  geom_point() +
  labs(y = NULL)
```

## Key words (without food/flies)

```{r}
tidy_stop %>%
  count(word, sort = TRUE) %>% filter(!word %in% c("food","flies"))%>%
  top_n(25) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word)) +
  geom_point() +
  labs(y = NULL)
```

## Let's get down and dirty with Lexicons

```{r}
get_sentiments("bing") %>% count(sentiment,sort =T) %>%
  ggplot(aes(x=reorder(sentiment,n),y=n)) + geom_col() +
  coord_flip()
```
```{r}
get_sentiments("nrc") %>% count(sentiment,sort =T) %>%
  ggplot(aes(x=reorder(sentiment,n),y=n)) + geom_col() +
  coord_flip()
```

#### Lexicon: Bing

```{r}
bing <- get_sentiments("bing")

tidy_bing <- tidy_stop %>% inner_join(bing)

tidy_bing %>% count(sentiment,sort = TRUE) %>%
  ggplot(aes(x=sentiment,y=n)) + geom_col()

```
```{r}
tidy_bing %>% count(word,sentiment,sort = TRUE) %>% top_n(20) %>%
  ggplot(aes(x=reorder(word,n),y=n,fill = sentiment)) + geom_col() +
  facet_wrap( ~sentiment,ncol=1) + coord_flip()

  
```

### Word Cloud

```{r}
library(wordcloud)
tidy_stop %>%
    count(word) %>%
  with(wordcloud(word, n, max.words = 100))

```

